Classifying Human Driving Behavior via Deep Neural Networks

### 2017-05-29 paper/paper-DrexelFormat.tex
updated paper - working on ch5

\subsection{Analysis Training LSTM in {\em second model} and {\em third model}}
The difference between {\em first model} and other models is that other models have AE. Therefore, AE layer from {\em second model} and {\em third model} caused worse performance. The first evidence of this can be found from training LSTM in both models. Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show the accuracy of the result from LSTM on each iterations during training. Figure \ref{fig:sae_loss} and Figure \ref{fig:mae_loss} show the loss (error) on each iterations during training. Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show the details of the train accuracy from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Table \ref{tbl:mae_16_accuracy}, Table \ref{tbl:mae_32_accuracy}, Table \ref{tbl:mae_64_accuracy}, Table \ref{tbl:mae_128_accuracy}, and Table \ref{tbl:mae_256_accuracy} show the details of the train accuracy from {\em third model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Training LSTM in {\em second model} and {\em third model} were slow and most cases did not reach accurach 1 (100\%) while the training LSTM in {\em first model} easily reached accuracy 1 (100\%). It implies that the data fed to LSTM had noise or problems. It also means that AE in {\em second model} and {\em third model} did not work correctly. The next subsection covers more detailed explanation about the error from AE in {\em second model} and {\em third model}.

@@

\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline

@@

\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline

@@

\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline

@@

\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline

@@

\multicolumn{2}{|c|}{Std}                   & 0.0208325   & 0.04781121248 & 0.08032837701 & 0.07375412734 & 0.08855229679 & \multicolumn{1}{l|}{0.1187070488} & \multicolumn{1}{l|}{0.1074483726} & 0.1325280456 & 0.1030488131 \\ \hline

@@

>>>>

\subsection{Analysis Training LSTM in {\em second model} and {\em third model}}
The difference between {\em first model} and other models is that other models have AE. Therefore, AE layer from {\em second model} and {\em third model} caused worse performance. The first evidence of this can be found during training LSTM in both models. Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show the accuracy of the result from LSTM on each iterations during training. Figure \ref{fig:sae_loss} and Figure \ref{fig:mae_loss} show the loss (error) on each iterations during training. Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show the details of the train accuracy from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Table \ref{tbl:sae_16_loss}, Table \ref{tbl:sae_32_loss}, Table \ref{tbl:sae_64_loss}, Table \ref{tbl:sae_128_loss}, and Table \ref{tbl:sae_256_loss} show the details of the train loss from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Table \ref{tbl:mae_16_accuracy}, Table \ref{tbl:mae_32_accuracy}, Table \ref{tbl:mae_64_accuracy}, Table \ref{tbl:mae_128_accuracy}, and Table \ref{tbl:mae_256_accuracy} show the details of the train accuracy from {\em third model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Table \ref{tbl:mae_16_loss}, Table \ref{tbl:mae_32_loss}, Table \ref{tbl:mae_64_loss}, Table \ref{tbl:mae_128_loss}, and Table \ref{tbl:mae_256_loss} show the details of the train loss from {\em third model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.

Training LSTM in {\em second model} and {\em third model} were slow and most cases did not reach accuracy 1 (100\%) while the training LSTM in {\em first model} easily reached accuracy 1 (100\%). It implies that the data fed to LSTM had noise or problems. It also means that AE in {\em second model} and {\em third model} did not work correctly. The next subsection covers more detailed explanation about the error from AE in {\em second model} and {\em third model}.

@@

\multirow{4}{*}{1}    & 1                   & 0.58333       & 0.66667     & 0.66667       & 0.75         & 0.75         & 0.83333                          & 1                                 & 0.91667      & 0.91667      \\ \cline{2-11} 
                      & 2                   & 0.5           & 0.5         & 0.66667       & 0.83333      & 0.83333      & 0.91667                          & 1                                 & 1            & 1            \\ \cline{2-11} 
                      & 3                   & 0.41667       & 0.58333     & 0.66667       & 0.91667      & 0.83333      & 0.83333                          & 0.91667                           & 1            & 0.91667      \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.58333     & 0.58333       & 0.58333      & 0.58333      & 0.75                             & 0.91667                           & 0.91667      & 0.91667      \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5           & 0.58333     & 0.5           & 0.5          & 0.5          & 0.58333                          & 0.75                              & 0.75         & 0.83333      \\ \cline{2-11} 
                      & 2                   & 0.5           & 0.58333     & 0.75          & 0.75         & 0.83333      & 0.91667                          & 1                                 & 1            & 1            \\ \cline{2-11} 
                      & 3                   & 0.5           & 0.66667     & 0.75          & 0.75         & 0.83333      & 0.91667                          & 0.83333                           & 0.83333      & 0.91667      \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.5         & 0.5           & 0.5          & 0.58333      & 0.5                              & 0.58333                           & 0.66667      & 0.66667      \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5           & 0.5         & 0.58333       & 0.58333      & 0.75         & 0.58333                          & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11} 
                      & 2                   & 0.5           & 0.41667     & 0.5           & 0.66667      & 0.66667      & 0.75                             & 0.75                              & 0.75         & 0.91667      \\ \cline{2-11} 
                      & 3                   & 0.5           & 0.33333     & 0.5           & 0.41667      & 0.5          & 0.58333                          & 0.91667                           & 0.75         & 0.75         \\ \cline{2-11} 
                      & 4                   & 0.33333       & 0.66667     & 0.66667       & 0.66667      & 0.83333      & 0.83333                          & 0.91667                           & 1            & 1            \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5           & 0.58333     & 0.58333       & 0.66667      & 0.75         & 0.83333                          & 0.83333                           & 0.83333      & 0.75         \\ \cline{2-11} 
                      & 2                   & 0.5           & 0.33333     & 0.66667       & 0.83333      & 0.66667      & 0.75                             & 0.75                              & 0.66667      & 0.83333      \\ \cline{2-11} 
                      & 3                   & 0.41667       & 0.58333     & 0.66667       & 0.66667      & 0.75         & 0.83333                          & 0.91667                           & 0.91667      & 0.91667      \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.41667     & 0.5           & 0.66667      & 0.75         & 0.75                             & 0.75                              & 0.83333      & 0.75         \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.484375      & 0.531249375 & 0.609375625   & 0.671875625  & 0.713540625  & 0.760415625                      & 0.838541875                       & 0.84895875   & 0.8697925    \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.05459200528 & 0.109185219 & 0.08985045449 & 0.1342629486 & 0.1177274886 & \multicolumn{1}{l|}{0.132201113} & \multicolumn{1}{l|}{0.1342647589} & 0.1187071365 & 0.1007786353 \\ \hline

@@

\multirow{4}{*}{1}    & 1                   & 0.41667       & 0.66667      & 0.91667      & 0.91667      & 0.83333      & 0.91667                          & 1                                 & 0.91667      & 1             \\ \cline{2-11} 
                      & 2                   & 0.5           & 0.75         & 0.66667      & 0.75         & 0.83333      & 1                                & 1                                 & 1            & 1             \\ \cline{2-11} 
                      & 3                   & 0.5           & 0.75         & 0.66667      & 0.75         & 0.91667      & 1                                & 0.91667                           & 0.58333      & 0.75          \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.58333      & 0.66667      & 0.66667      & 0.91667      & 0.91667                          & 1                                 & 1            & 1             \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5           & 0.75         & 0.83333      & 0.83333      & 0.91667      & 1                                & 0.91667                           & 0.91667      & 1             \\ \cline{2-11} 
                      & 2                   & 0.41667       & 0.58333      & 0.83333      & 0.91667      & 1            & 0.91667                          & 1                                 & 0.91667      & 1             \\ \cline{2-11} 
                      & 3                   & 0.5           & 0.66667      & 0.58333      & 0.66667      & 0.66667      & 0.66667                          & 0.75                              & 0.75         & 0.83333       \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.33333      & 0.41667      & 0.5          & 0.5          & 0.83333                          & 0.58333                           & 0.83333      & 0.83333       \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.33333       & 0.75         & 0.83333      & 0.91667      & 0.91667      & 1                                & 1                                 & 1            & 1             \\ \cline{2-11} 
                      & 2                   & 0.5           & 0.66667      & 0.75         & 0.91667      & 0.83333      & 1                                & 0.83333                           & 1            & 1             \\ \cline{2-11} 
                      & 3                   & 0.58333       & 0.66667      & 0.83333      & 0.91667      & 1            & 0.83333                          & 0.91667                           & 0.83333      & 1             \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.5          & 0.58333      & 0.66667      & 0.83333      & 0.91667                          & 1                                 & 0.75         & 1             \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5           & 0.5          & 0.5          & 0.83333      & 0.66667      & 0.83333                          & 0.83333                           & 0.83333      & 0.83333       \\ \cline{2-11} 
                      & 2                   & 0.5           & 0.58333      & 0.75         & 0.75         & 0.75         & 0.75                             & 0.83333                           & 0.83333      & 0.91667       \\ \cline{2-11} 
                      & 3                   & 0.5           & 0.5          & 0.58333      & 0.58333      & 0.75         & 0.83333                          & 0.83333                           & 0.91667      & 0.91667       \\ \cline{2-11} 
                      & 4                   & 0.33333       & 0.58333      & 0.75         & 0.91667      & 0.91667      & 1                                & 1                                 & 1            & 1             \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.473958125   & 0.614583125  & 0.69791625   & 0.78125125   & 0.828125625  & 0.901041875                      & 0.90104125                        & 0.880208125  & 0.942708125   \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.06610021505 & 0.1173602203 & 0.1390271423 & 0.1356577598 & 0.1342634141 & \multicolumn{1}{l|}{0.101920437} & \multicolumn{1}{l|}{0.1187085405} & 0.1177294942 & 0.08454060225 \\ \hline

@@

\multirow{4}{*}{1}    & 1                   & 0.5           & 0.58333     & 0.66667     & 0.66667      & 0.75       & 0.83333                           & 1                                  & 1             & 0.66667      \\ \cline{2-11} 
                      & 2                   & 0.66667       & 0.66667     & 0.83333     & 0.91667      & 0.91667    & 0.41667                           & 0.75                               & 0.66667       & 0.5          \\ \cline{2-11} 
                      & 3                   & 0.5           & 0.5         & 0.66667     & 0.91667      & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.75        & 0.66667     & 0.83333      & 0.91667    & 0.91667                           & 0.91667                            & 1             & 1            \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.58333       & 0.83333     & 0.83333     & 0.66667      & 0.66667    & 0.66667                           & 0.83333                            & 0.83333       & 0.83333      \\ \cline{2-11} 
                      & 2                   & 0.5           & 0.5         & 0.75        & 0.91667      & 0.58333    & 0.83333                           & 1                                  & 1             & 1            \\ \cline{2-11} 
                      & 3                   & 0.5           & 0.58333     & 0.91667     & 1            & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.66667     & 0.91667     & 0.83333      & 0.91667    & 1                                 & 0.91667                            & 0.91667       & 0.91667      \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.58333       & 0.83333     & 0.91667     & 1            & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11} 
                      & 2                   & 0.5           & 0.58333     & 0.5         & 0.66667      & 0.75       & 0.83333                           & 0.75                               & 0.91667       & 0.83333      \\ \cline{2-11} 
                      & 3                   & 0.58333       & 0.75        & 0.91667     & 0.91667      & 1          & 0.91667                           & 1                                  & 1             & 1            \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.66667     & 0.75        & 0.83333      & 0.91667    & 0.91667                           & 0.91667                            & 0.91667       & 1            \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.58333       & 0.66667     & 0.83333     & 0.91667      & 1          & 0.91667                           & 0.91667                            & 0.91667       & 1            \\ \cline{2-11} 
                      & 2                   & 0.41667       & 0.75        & 0.83333     & 0.91667      & 0.83333    & 0.83333                           & 0.91667                            & 0.91667       & 0.91667      \\ \cline{2-11} 
                      & 3                   & 0.5           & 0.91667     & 0.83333     & 0.91667      & 1          & 1                                 & 1                                  & 1             & 1            \\ \cline{2-11} 
                      & 4                   & 0.41667       & 0.83333     & 0.91667     & 1            & 0.58333    & 0.75                              & 0.83333                            & 0.83333       & 1            \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.520833125   & 0.692708125 & 0.796875625 & 0.869793125  & 0.86458375 & 0.86458375                        & 0.921875625                        & 0.9322925     & 0.916666875  \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.06454864664 & 0.124419997 & 0.12159725  & 0.1137275314 & 0.1517652  & \multicolumn{1}{l|}{0.1547843482} & \multicolumn{1}{l|}{0.08855225756} & 0.09238947353 & 0.1459323791 \\ \hline

@@

\multirow{4}{*}{1}    & 1                   & 0.5           & 0.66667       & 0.91667       & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11} 
                      & 2                   & 0.58333       & 0.75          & 0.83333       & 1           & 0.91667       & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11} 
                      & 3                   & 0.5           & 0.58333       & 0.75          & 0.83333     & 0.83333       & 0.91667                            & 0.91667                            & 0.83333      & 0.91667       \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.75          & 1             & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5           & 0.66667       & 0.83333       & 0.83333     & 0.75          & 1                                  & 0.91667                            & 0.83333      & 1             \\ \cline{2-11} 
                      & 2                   & 0.5           & 0.83333       & 0.83333       & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11} 
                      & 3                   & 0.41667       & 0.66667       & 0.83333       & 0.83333     & 0.91667       & 1                                  & 1                                  & 0.66667      & 0.83333       \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.5           & 0.66667       & 0.83333     & 0.83333       & 0.91667                            & 1                                  & 0.58333      & 0.83333       \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.41667       & 0.75          & 0.83333       & 1           & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11} 
                      & 2                   & 0.5           & 0.66667       & 0.66667       & 0.83333     & 1             & 0.75                               & 0.91667                            & 0.91667      & 0.91667       \\ \cline{2-11} 
                      & 3                   & 0.5           & 0.75          & 0.83333       & 0.91667     & 1             & 1                                  & 1                                  & 1            & 1             \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.5           & 0.83333       & 1           & 1             & 1                                  & 1                                  & 1            & 0.75          \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.66667       & 0.66667       & 0.91667       & 1           & 0.91667       & 1                                  & 1                                  & 0.75         & 0.83333       \\ \cline{2-11} 
                      & 2                   & 0.41667       & 0.75          & 0.83333       & 0.91667     & 0.91667       & 1                                  & 0.83333                            & 1            & 1             \\ \cline{2-11} 
                      & 3                   & 0.5           & 0.75          & 0.75          & 0.83333     & 0.91667       & 0.91667                            & 0.91667                            & 1            & 1             \\ \cline{2-11} 
                      & 4                   & 0.5           & 0.83333       & 0.83333       & 0.91667     & 0.91667       & 0.91667                            & 1                                  & 0.91667      & 1             \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.500000625   & 0.69270875    & 0.822915625   & 0.921874375 & 0.9322925     & 0.9635425                          & 0.968750625                        & 0.90625      & 0.942708125   \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.06085745339 & 0.09962245864 & 0.08539068716 & 0.077393879 & 0.07588246275 & \multicolumn{1}{l|}{0.06782780487} & \multicolumn{1}{l|}{0.05159461826} & 0.1356572478 & 0.08454060225 \\ \hline

@@

\multirow{4}{*}{1}    & 1                   & 0.5 & 0.66667      & 0.83333      & 0.83333       & 1             & 1                                  & 0.83333                            & 0.91667       & 0.91667      \\ \cline{2-11} 
                      & 2                   & 0.5 & 0.5          & 0.83333      & 0.83333       & 0.83333       & 0.91667                            & 1                                  & 1             & 1            \\ \cline{2-11} 
                      & 3                   & 0.5 & 0.66667      & 0.83333      & 0.83333       & 0.83333       & 0.91667                            & 1                                  & 1             & 1            \\ \cline{2-11} 
                      & 4                   & 0.5 & 0.66667      & 0.66667      & 0.91667       & 0.91667       & 0.91667                            & 1                                  & 0.91667       & 1            \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5 & 0.5          & 0.58333      & 0.91667       & 1             & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11} 
                      & 2                   & 0.5 & 0.5          & 0.75         & 0.91667       & 0.91667       & 0.91667                            & 1                                  & 1             & 0.91667      \\ \cline{2-11} 
                      & 3                   & 0.5 & 0.75         & 0.75         & 1             & 0.83333       & 1                                  & 1                                  & 0.91667       & 0.91667      \\ \cline{2-11} 
                      & 4                   & 0.5 & 0.5          & 0.66667      & 1             & 1             & 1                                  & 0.66667                            & 1             & 1            \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5 & 0.5          & 0.5          & 0.83333       & 0.91667       & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11} 
                      & 2                   & 0.5 & 0.75         & 0.91667      & 1             & 0.91667       & 0.75                               & 0.91667                            & 1             & 1            \\ \cline{2-11} 
                      & 3                   & 0.5 & 0.83333      & 0.75         & 0.75          & 0.91667       & 0.91667                            & 0.91667                            & 1             & 0.91667      \\ \cline{2-11} 
                      & 4                   & 0.5 & 0.58333      & 0.83333      & 0.83333       & 1             & 0.91667                            & 1                                  & 1             & 1            \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5 & 0.66667      & 0.83333      & 0.91667       & 1             & 0.91667                            & 1                                  & 0.91667       & 0.91667      \\ \cline{2-11} 
                      & 2                   & 0.5 & 0.66667      & 0.91667      & 1             & 1             & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11} 
                      & 3                   & 0.5 & 0.66667      & 0.91667      & 0.91667       & 1             & 1                                  & 1                                  & 1             & 1            \\ \cline{2-11} 
                      & 4                   & 0.5 & 0.58333      & 0.66667      & 0.75          & 0.83333       & 0.83333                            & 0.83333                            & 0.91667       & 0.66667      \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.5 & 0.625000625  & 0.765625     & 0.890625      & 0.932291875   & 0.93750125                         & 0.947916875                        & 0.973959375   & 0.95312625   \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0   & 0.1054095189 & 0.1225453431 & 0.08454097192 & 0.06951486989 & \multicolumn{1}{l|}{0.07136227349} & \multicolumn{1}{l|}{0.09562148083} & 0.03989120044 & 0.0858968212 \\ \hline

@@

%%%%
\caption{SAE, 16 Neuron Training Loss}
\label{tbl:sae_16_loss}
\multirow{4}{*}{1}    & 1                   & 0.867708     & 0.658836     & 0.598745      & 0.570216      & 0.542723     & 0.509277     & 0.45653      & 0.371586     & 0.312368     \\ \cline{2-11} 
                      & 2                   & 0.716154     & 0.647359     & 0.5802        & 0.466887      & 0.368403     & 0.189879     & 0.138792     & 0.082835     & 0.039202     \\ \cline{2-11} 
                      & 3                   & 1.010004     & 0.726795     & 0.639507      & 0.557821      & 0.456062     & 0.357702     & 0.248903     & 0.18167      & 0.161653     \\ \cline{2-11} 
                      & 4                   & 0.931758     & 0.679017     & 0.68355       & 0.653738      & 0.627172     & 0.579391     & 0.47901      & 0.330892     & 0.283151     \\ \hline
\multirow{4}{*}{2}    & 1                   & 1.034264     & 0.750502     & 0.690592      & 0.664423      & 0.644417     & 0.615162     & 0.566874     & 0.49449      & 0.404689     \\ \cline{2-11} 
                      & 2                   & 0.734266     & 0.668139     & 0.599754      & 0.502355      & 0.373805     & 0.255638     & 0.172213     & 0.113529     & 0.033831     \\ \cline{2-11} 
                      & 3                   & 0.71177      & 0.633562     & 0.587044      & 0.53257       & 0.460952     & 0.337656     & 0.394645     & 0.232444     & 0.165801     \\ \cline{2-11} 
                      & 4                   & 2.372197     & 1.381874     & 0.749318      & 0.757406      & 0.706545     & 0.682112     & 0.663386     & 0.640868     & 0.617737     \\ \hline
\multirow{4}{*}{3}    & 1                   & 1.073245     & 0.739515     & 0.660751      & 0.643766      & 0.618173     & 0.586885     & 0.546323     & 0.490365     & 0.408254     \\ \cline{2-11} 
                      & 2                   & 0.920753     & 0.752893     & 0.69619       & 0.671112      & 0.643913     & 0.598275     & 0.513106     & 0.447455     & 0.401655     \\ \cline{2-11} 
                      & 3                   & 1.307593     & 0.805894     & 0.766722      & 0.712964      & 0.688656     & 0.663078     & 0.635468     & 0.601089     & 0.554527     \\ \cline{2-11} 
                      & 4                   & 0.798854     & 0.695754     & 0.623671      & 0.542144      & 0.401806     & 0.282288     & 0.181928     & 0.127126     & 0.067818     \\ \hline
\multirow{4}{*}{4}    & 1                   & 1.406092     & 0.650761     & 0.644504      & 0.618038      & 0.589857     & 0.561498     & 0.51978      & 0.463588     & 0.389386     \\ \cline{2-11} 
                      & 2                   & 1.086467     & 0.74607      & 0.68114       & 0.656806      & 0.624859     & 0.583237     & 0.508703     & 0.532442     & 0.473402     \\ \cline{2-11} 
                      & 3                   & 0.755674     & 0.690224     & 0.650469      & 0.615333      & 0.559955     & 0.472473     & 0.328977     & 0.178266     & 0.138556     \\ \cline{2-11} 
                      & 4                   & 0.961943     & 0.72807      & 0.661066      & 0.639339      & 0.616993     & 0.595482     & 0.572181     & 0.538515     & 0.473751     \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 1.043046375  & 0.7472040625 & 0.6570764375  & 0.612807375   & 0.5577681875 & 0.4918770625 & 0.4329261875 & 0.3641975    & 0.3078613125 \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.4075305729 & 0.1758645423 & 0.05392737257 & 0.07834639722 & 0.1112575624 & 0.1562129618 & 0.1693802095 & 0.1872028666 & 0.1866248047 \\ \hline
\caption{SAE, 32 Neuron Training Loss}
\label{tbl:sae_32_loss}
\multirow{4}{*}{1}    & 1                   & 1.089936     & 0.623444      & 0.401044     & 0.163081    & 0.289254     & 0.169454     & 0.183729     & 0.146472     & 0.126548     \\ \cline{2-11} 
                      & 2                   & 0.742237     & 0.526604      & 0.439773     & 0.324494    & 0.287876     & 0.198892     & 0.126902     & 0.071317     & 0.033964     \\ \cline{2-11} 
                      & 3                   & 0.767949     & 0.61231       & 0.516521     & 0.406594    & 0.170029     & 0.06262      & 0.229247     & 0.858627     & 0.415347     \\ \cline{2-11} 
                      & 4                   & 1.053317     & 0.659953      & 0.596998     & 0.531688    & 0.38192      & 0.164083     & 0.024379     & 0.007555     & 0.004247     \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.689631     & 0.574641      & 0.428335     & 0.273611    & 0.146224     & 0.057889     & 0.212958     & 0.164516     & 0.081435     \\ \cline{2-11} 
                      & 2                   & 0.800932     & 0.656356      & 0.552568     & 0.434933    & 0.272102     & 0.248611     & 0.085569     & 0.161704     & 0.030388     \\ \cline{2-11} 
                      & 3                   & 3.028554     & 0.669358      & 0.703512     & 0.653291    & 0.614116     & 0.592589     & 0.563766     & 0.519461     & 0.422753     \\ \cline{2-11} 
                      & 4                   & 2.444665     & 0.850118      & 0.751037     & 0.726684    & 0.676912     & 0.631111     & 0.585235     & 0.535744     & 0.45477      \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.814303     & 0.571832      & 0.461643     & 0.260355    & 0.101084     & 0.006807     & 0.0016       & 0.000778     & 0.000545     \\ \cline{2-11} 
                      & 2                   & 0.758862     & 0.564178      & 0.444358     & 0.265892    & 0.501366     & 0.189026     & 0.207664     & 0.127553     & 0.07445      \\ \cline{2-11} 
                      & 3                   & 0.698428     & 0.61994       & 0.48369      & 0.272926    & 0.089773     & 0.304789     & 0.266858     & 0.189368     & 0.118763     \\ \cline{2-11} 
                      & 4                   & 0.963418     & 0.706397      & 0.659662     & 0.611685    & 0.55393      & 0.450733     & 0.266549     & 0.301658     & 0.190811     \\ \hline
\multirow{4}{*}{4}    & 1                   & 2.152231     & 0.717714      & 0.595703     & 0.580464    & 0.532885     & 0.490875     & 0.445372     & 0.393754     & 0.344004     \\ \cline{2-11} 
                      & 2                   & 0.743162     & 0.614233      & 0.557129     & 0.473301    & 0.375491     & 0.265379     & 0.370009     & 0.275214     & 0.189347     \\ \cline{2-11} 
                      & 3                   & 1.251604     & 0.795482      & 0.719207     & 0.64731     & 0.555575     & 0.41519      & 0.282817     & 0.220768     & 0.173061     \\ \cline{2-11} 
                      & 4                   & 0.746536     & 0.583235      & 0.468734     & 0.333579    & 0.161202     & 0.051078     & 0.032621     & 0.011396     & 0.003485     \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 1.171610313  & 0.6466121875  & 0.548744625  & 0.434993    & 0.3568586875 & 0.268695375  & 0.2428296875 & 0.2491178125 & 0.166494875  \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.7166649491 & 0.08658560248 & 0.1123084497 & 0.173138938 & 0.1950394115 & 0.1960940258 & 0.1778117104 & 0.2314791816 & 0.1590537111 \\ \hline
\caption{SAE, 64 Neuron Training Loss}
\label{tbl:sae_64_loss}
\multirow{4}{*}{1}    & 1                   & 1.916317     & 0.653356      & 0.605663     & 0.55996      & 0.503468     & 0.401758     & 0.222751     & 0.055338     & 0.76406      \\ \cline{2-11} 
                      & 2                   & 0.706926     & 0.583445      & 0.375156     & 0.236676     & 0.282038     & 1.71037      & 0.790081     & 0.978644     & 1.609758     \\ \cline{2-11} 
                      & 3                   & 2.448815     & 0.698517      & 0.612111     & 0.463534     & 0.290417     & 0.068782     & 0.01157      & 0.002706     & 0.001282     \\ \cline{2-11} 
                      & 4                   & 2.6282       & 0.650327      & 0.555985     & 0.400741     & 0.196832     & 0.171271     & 0.122514     & 0.079407     & 0.063133     \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.936053     & 0.522095      & 0.299643     & 0.727932     & 0.605426     & 0.539633     & 0.477041     & 0.398771     & 0.345885     \\ \cline{2-11} 
                      & 2                   & 0.934966     & 0.700015      & 0.532452     & 0.33672      & 0.903183     & 0.290494     & 0.175402     & 0.105801     & 0.038551     \\ \cline{2-11} 
                      & 3                   & 0.909634     & 0.611419      & 0.275903     & 0.04429      & 0.091263     & 0.020732     & 0.005012     & 0.013919     & 0.003368     \\ \cline{2-11} 
                      & 4                   & 0.73965      & 0.542199      & 0.374967     & 0.301242     & 0.162709     & 0.07067      & 0.331129     & 0.197377     & 0.178295     \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.858011     & 0.552013      & 0.290431     & 0.106647     & 0.046936     & 0.11011      & 0.034987     & 0.008316     & 0.003274     \\ \cline{2-11} 
                      & 2                   & 1.860844     & 0.754264      & 0.688465     & 0.626176     & 0.57389      & 0.485814     & 0.460241     & 0.281851     & 0.22003      \\ \cline{2-11} 
                      & 3                   & 0.855587     & 0.466632      & 0.278699     & 0.185195     & 0.121497     & 0.162509     & 0.073815     & 0.032642     & 0.009956     \\ \cline{2-11} 
                      & 4                   & 1.247114     & 0.655767      & 0.441917     & 0.315909     & 0.21307      & 0.181635     & 0.131997     & 0.111561     & 0.103416     \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.810931     & 0.559138      & 0.428732     & 0.278943     & 0.1103       & 0.184967     & 0.156358     & 0.114446     & 0.101546     \\ \cline{2-11} 
                      & 2                   & 0.888711     & 0.587507      & 0.463251     & 0.222382     & 0.249457     & 0.303939     & 0.240719     & 0.174783     & 0.131379     \\ \cline{2-11} 
                      & 3                   & 0.88148      & 0.422646      & 0.233577     & 0.170769     & 0.054713     & 0.007352     & 0.001849     & 0.000536     & 0.000282     \\ \cline{2-11} 
                      & 4                   & 0.740278     & 0.443124      & 0.180983     & 0.054872     & 0.711295     & 0.512839     & 0.443325     & 0.440904     & 0.418722     \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 1.210219813  & 0.587654      & 0.4148709375 & 0.31449925   & 0.319780875  & 0.3264296875 & 0.2299244375 & 0.187312625  & 0.2495585625 \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.6338026386 & 0.09569099933 & 0.1515519752 & 0.1992396693 & 0.2597535716 & 0.4077697387 & 0.2200004192 & 0.2511534118 & 0.4161462485 \\ \hline
\caption{SAE, 128 Neuron Training Loss}
\label{tbl:sae_128_loss}
\multirow{4}{*}{1}    & 1                   & 0.72861      & 0.560893      & 0.311639      & 0.050086     & 0.000617     & 0.000069     & 0.000042     & 0.000024     & 0.000018     \\ \cline{2-11} 
                      & 2                   & 1.315017     & 0.443847      & 0.298309      & 0.16871      & 0.103412     & 0.054363     & 0.025967     & 0.031268     & 0.014162     \\ \cline{2-11} 
                      & 3                   & 2.498684     & 0.637791      & 0.471613      & 0.357605     & 0.269624     & 0.135875     & 0.321816     & 0.217548     & 0.148613     \\ \cline{2-11} 
                      & 4                   & 2.034755     & 0.518702      & 0.432506      & 0.297452     & 0.168139     & 0.093127     & 0.026231     & 0.003216     & 0.001189     \\ \hline
